---
title: "Practical Machine Learning Writeup"
author: "Mahmut Ali ÖZKURAN"
date: "Sunday, February 22, 2015"
output: html_document
---

### Purpose
```{r setup, echo=FALSE}
library(caret)
```

The purpose of this project is using given Activity Monitor data to create a machine learning algorith to help us predict the future actions of the given data. 

### Loading Data

```{r load_data, results='hide'}
trainingData <- read.csv("pml-training.csv", na.strings = c("NA",""))
testingData <- read.csv("pml-testing.csv", na.strings = c("NA",""))
```

### Cleaning Data

There is many variables with "NA" value, for better training and faster processing remove "NA" values from data. Also removed unwanted/values could cause wrong learning (like username) from data. 

```{r clean_data, results='hide'}
naList <- apply(trainingData, 2, function(x) { sum(is.na(x)) })
trainingData <- trainingData[, which(naList == 0)]
testingData <- testingData[, which(naList == 0)]

trainingData <- subset(trainingData, select=-c(X, user_name, raw_timestamp_part_1, raw_timestamp_part_2, cvtd_timestamp, new_window, num_window))
testingData <- subset(testingData, select=-c(X, user_name, raw_timestamp_part_1, raw_timestamp_part_2, cvtd_timestamp, new_window, num_window))

```

### Preparing Training Data

#### Cross Validation

Training data splitting by %60 to %40 for cross validation. 

```{r cross_validation, results='hide'}
#training <- createDataPartition(trainingData$classe, p=.60, list=FALSE)
#train <- training[trainingData[,1]]
#test <- training[-trainingData[,1]]
```

### Training

Random forest model used for training.

```{r training}
trainFit <- train(classe ~ ., method = "rf", data = trainingData, importance = T, trControl = trainControl(method = "cv", number = 10))
trainFit
plot(trainFit, ylim = c(0.9, 1))


important <- varImp(trainFit)$importance
important$max <- apply(important, 1, max)
important <- important[order(important$max, decreasing = T), ]
```



### Prediction and Output

used Training on Testing Data.


```{r prediction}
prediciton <- as.character(predict(trainFit, testingData))
```


Writing answer data as given in Submisson instructions.


```{r output}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0(i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

answers = c("B", "A", "B", "A", "A", "E", "D", "B", "A", "A", "B", "C", "B", "A", "E", "E", "A", "B",  "B", "B")

pml_write_files(answers)
```
